High-Dimensional Regularized Discriminant Analysis

### 2015-12-14 reports/paper-hdrda.Rnw
Added Phil's writeup of first sims

>>>>

\subsubsection{Results}

As expected, regardless of the values of $p$, $\rho$, or $\bm \mu$, as the
contaminated probability increases, the average error rate increases.  Also, as
can be expected, the average error rates were typically higher for $\bm \mu=0.5$
than for $\bm \mu=1$. The difference in the average error rates for the methods
of Pang, Tong, and Witten all yielded increasingly higher average error rates
than HDRDA ridge, HDRDA complex, Guo, or random forests as the contaminated
probability increased. The correlation coefficient appears to have had little,
if any, effect on the average error rates for any of the considered classifiers.

Regardless of the value of $rho$, $p$, or $\bm \mu$, random forests consistently
yielded the highest average error rate, and the average error rate for random
forests was much more pronounced when $\bm \mu=0.5$. However, as the
contaminated probability increased, random forests became increasingly
competitive, and, in some cases, e.g, $\bm \mu=0.5$, $p=100$, and contaminated
probability greater than 0.05 yielded the lowest average error rate.

Pang and Tong's methods yielded practically the same and consistently the worst
average error rates when the contaminated probability was greater than 0,
regardless of the value of $\bm \mu$, $p$, or $\rho$. Witten's method performed
only slightly better as the contaminated probability increased, however, when
$\bm \mu = 0.5$, Witten's method became increasingly competitive with Pang and
Tong for yielding the highest average error rate as $p$ increased.

Guo's method always outperformed Pang, Witten, and Tong, but never outperformed
the HDRDA methods. For the considered parameter configurations, Guo's method
performed similarly to random forests when the contaminated probability was
greater than 0 and yielded similar results to HDRDA ridge, HDRDA convex when the
contaminated probability was equal to 0. However, as the contaminated
probability increased, Guo's method was often outperformed by HDRDA ridge, HDRDA
convex, and random forests.

HDRDA ridge and HDRDA complex yielded the lowest average error rates, regardless
of the value of $\bm \mu$, $p$, or $\rho$, with HDRDA ridge typically
outperforming HDRDA complex when the contaminated probability was greater than
0. HDRDA ridge only seemed to have competition with random forests when the
contaminated probability was 0.20. Moreover, neither HDRDA ridge nor HDRDA
complex seem to be affected by $p$.
